---
title             : "Lab 8"
shorttitle        : "This is the assigment of lab 8"

author: 
  - name          : "Teresa Chen"
    affiliation   : "3"
    corresponding : yes    # Define only one corresponding author
    address       : "Rm.52 Gerlnger Annex, University of Oregon, OR 97403"
    email         : "szuhuac@uoregon.edu"
  - name          : "Jun Lun"
    affiliation   : "2"
  - name          : "Steffi Hung"
    affiliation   : "2"
  - name          : "Ting-fen Lin"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Human Physiology"
  - id            : "2"
    institution   : "Department of East Asia Linguistic Language"
  - id            : "3"
    institution   : "Department of Communication Disorder"
    


abstract: |
  This is an abstract.
  
 
  
keywords          : "math, reading, free lunch"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library("tidyverse")
library("rio")
library("here")
library("janitor")
library("ggplot2")
library("skimr")
library("knitr")
library("kableExtra")
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      error = TRUE,
                      fig.width = 6.5,
                      fig.height = 8
                      )
theme_set(theme_minimal(base_size = 8))
```

```{r load_data}
df <- import(here("data", "star.csv"),
                   setclass = "tbl_df")
```


# Methods

## Participants

## Material

## Procedure

## Data analysis

# Results
```{r commit 3, results='asis'}

df %>% 
  group_by(sex, frl) %>% 
  summarize(math_mean = mean(tmathss), 
            math_sd = sd(tmathss),
            rdg_mean = mean(treadss),
            rdg_sd = sd(treadss)) %>% 
  kable(format = "latex", digits = 2, booktabs = T)
  
  
```

```{r figure}
df %>% 
  ggplot(aes(x = totexp, y = tmathss)) +
   geom_point(color = "gray50") +
    geom_smooth(aes(color = frl), method = lm) +
    labs(x = "Teacher Experience (years)",
         y = "Total Math Scale Score",
         title = "Relation between teacher experience and math scores",
         subtitle = "Separate regression lines displayed by free/redued price lunch status"
    ) +
    scale_color_discrete(name = "Lunch status",
                         breaks = c("yes", "no"),
                       labels = c("Free/Reduced Price Meals","Paid Meals")) +
  theme(legend.position = "bottom")

```
According to the figure, teachers' experience does not play an important role on students' math performance but students' social economic status (SES) does. Student with a lower SES status, indicated by having a free/reduced lunch, has a lower math score compared to those who have high SES status. 

# Discussion
Vowel space is complex (see @logemann1998evaluation)
@munro1996effects reported that vowel space and language acquisition are closely related 



\newpage

# References



\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
