---
title             : "Vowel Space"
shorttitle        : "SKY"

author: 
  - name          : "Teresa Chen"
    affiliation   : "3"
    corresponding : yes    # Define only one corresponding author
    address       : "Rm.52 Gerlnger Annex, University of Oregon, OR 97403"
    email         : "szuhuac@uoregon.edu"
  - name          : "Jun Lun"
    affiliation   : "2"
  - name          : "Steffi Hung"
    affiliation   : "2"
  - name          : "Ting-fen Lin"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Human Physiology"
  - id            : "2"
    institution   : "Department of East Asia Linguistic Language"
  - id            : "3"
    institution   : "Department of Communication Disorder"
    


abstract: |
  This is an abstract.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "vowel, Mandarin"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library("tidyverse")
library("rio")
library("here")
library("janitor")
library("ggplot2")
library("skimr")
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      error = TRUE,
                      fig.width = 6.5,
                      fig.height = 8
                      )
theme_set(theme_minimal(base_size = 8))
```

```{r load_data}
df <- import(here("data", "star.csv"),
                   setclass = "tbl_df")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("references.bib")` for all our analyses.


# Results
```{r}
head(df)
df %>% 
  group_by(sex, frl, tmathss, treadss) %>% 
  summarize(mean = mean(tmathss), 
            sd = sd(tmathss),
            mean = mean(treadss),
            sd = sd(treadss)) %>% 
  knitr::kable(format = "latex")
```

# Discussion
Vowel space is complex (see @logemann1998evaluation)
@munro1996effects reported that vowel space and language acquisition are closely related 



\newpage

# References



\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
